Verifying Demonstrations

### 2020-03-03 paper/DB-Schnorr-UWB.tex
Fixes order of properties in section title
Reorders UWB: puts proofs last

@@

\subsection{\acs*{DBMF}, \acs*{DBDH} and \acs*{DBTF} resistance}

@@

\Acl{DB} protocols requires hardware implementations.
We will use a \emph{trusted} hardware implementation to overcome the limitation 
of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
We will need \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
any two devices in this \ac{PKI} to perform \acl{DB}.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which \emph{simultaneously} proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
\item that that knowledge is within proximity.
\end{enumerate*}

We will now introduce an extended protocol, \(\DBSHW\), which represents the 
secure hardware implementation.
\Cref{DBSHW-overview} presents an overview.

    Static \(\sk_P, \cert_P\colon \pk_P = \hat g^{\sk_P}\)
    &
    & \(\sk_V, \pk_V = \hat g^{\sk_V}\)\\

    \(\cert_P\)
    & \(\ProtoSendRight{\cert_P}\)
    & \(k \gets \pk_P^{\sk_V}\)
    \\

The \(\DBSHW\) secure hardware device must contain a (static) private 
key~\(\sk_P\) (for the prover, \(\sk_V\) for the verifier) with a digital 
certificate~\(\cert_P\) (and \(\cert_V\)) for the public key~\(\pk_P\) (and 
\(\pk_V\)).

>>>>

All \acl{DB} protocols requires hardware 
implementations~\cite{DBonSmartphones}.
We will use a \emph{trusted} hardware implementation to overcome the limitation 
of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
We will need \iac{PKI} for the verifier to verify the trusted hardware.
We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
any two devices in this \ac{PKI} to perform \acl{DB}.
With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
\ac{ZKPK} which \emph{simultaneously} proves
\begin{enumerate*}
\item that the protocol is run by trusted hardware,
\item that that trusted hardware is within proximity,
\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
\item that that knowledge is within proximity.
\end{enumerate*}

We will now introduce an extended protocol, \(\DBSHW\), which represents the 
secure hardware implementation.
The \ac{PKI} is based on CL04~\cite{CLsignatures} signatures.
\Cref{DBSHW-overview} presents an overview.

    \multicolumn{2}{l}{%
      Static \(\hat g, \hat q, \sk_P\in \ZZ_q, \pk_P = \hat g^{\sk_P}, \sigma\)
    }
    & Static \(\hat g, \hat q\)
    \\

    \(x\rgets \ZZ_q\)
    & \(\ProtoSendRight{g^x}\)
    & \(k \gets \pk_P^{\sk_V}\)
    \\

The \(\DBSHW\) secure hardware device must contain a (static) private 
key~\(\sk_P\) for the prover with a digital certificate~\(\cert_P\) (and 
\(\cert_V\)) for the public key~\(\pk_P\) (and \(\pk_V\)).

@@

\subsection{\acs*{DBMF}, \acs*{DBTF} and \acs*{DBDH} resistance}

@@
